Developing a preprint culture in biology

### 2012-10-11 ms.tex
editing, title

\title{Developing a public preprint culture in biology}

@@

%%% TP Oct 11 2012
%%% Just something I am thinking about now
%%% We are not a good sample of biologists. We are mostly evolutionary ecologists,
%%% and perhaps having the input of a "real" (labcoat wearing) biologist can help.

@@

In contrast to other disciplines, the field of biology has effectively no
%%% TP
%%% As good a place as any to define biology... PLoS Biology, for example,
%%% is mostly cell biol stuff. We are not a typical subset of biologists!
preprint culture, with the exception of small pockets of primarily highly
quantitative research (\emph{e.g.}, epidemiology, population genetics).
Submitting to preprint servers has become more common in the past few years,
and the quantitative biology section in arXiv is experiencing the fastest
growth in submissions \cite{cal12}. Yet, the number of biology papers
submitted to preprint servers still represents only a small fraction of the
total research produced in biology.

There are a number of reasons that biologists have not traditionally had a
culture of sharing preprints, many of which are based on common misconceptions
regarding the costs and benefits associated with the practice. For example, in contrast
to other fields there is a perception in biology that public preprints
make it easier to steal ideas. However, there is no evidence of this happening
in the numerous other fields that have adopted preprint servers, and since preprint
servers create a clear record of who had the idea first, and when, this
appears to be a largely unfounded concern. In other fields preprints serve the
opposite role, they allow straightforward establishment of precedence, letting
research lay claim to an idea thus preventing it from being "stolen" \cite{gin11}
%%% TP
%%% Most refs will ask for a ref at that point. At least, I will, but I'm so
%%% demanding that I'm part of why the review process sucks ;-)

>>>>

\title{Developing a preprint culture in biology}

@@

@@

In contrast to other disciplines, the field of biology has effectively no
preprint culture, with the exception of small pockets of primarily highly
quantitative research (\emph{e.g.}, epidemiology, population genetics).
Submitting to preprint servers has become more common in the past few years,
and the quantitative biology section in arXiv is experiencing the fastest
growth in submissions \cite{cal12}. Yet, the number of biology papers
submitted to preprint servers still represents only a small fraction of the
total research produced in biology.

There are a number of reasons that biologists have not traditionally had a
culture of sharing preprints, many of which are based on common misconceptions
regarding the costs and benefits associated with the practice. For example, in contrast
to other fields there is a perception in biology that public preprints
make it easier to steal ideas. However, there is no evidence of this happening
in the numerous other fields that have adopted preprint servers, and since preprint
servers create a clear record of who had the idea first, and when, this
appears to be a largely unfounded concern. In other fields preprints serve the
opposite role, they allow straightforward establishment of precedence, letting
research lay claim to an idea thus preventing it from being "stolen" \cite{gin11}
